---
author: "Akanksha Utreja, Swapnil Vermani"
date: "November 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Q1.Segment respondents based on the Partworth data (use any unsupervised learning technique). 

####Solution:


```{r cars}
#Load Data

partdata <- read.csv("C://Users//AKANKSHA//Desktop//ISB CBA//Marketing Analytics//Partworth Data.csv", header = TRUE, sep = ",")
#partdata[1] <- NULL
head(partdata)
dim(partdata)
normalized_data <- scale(partdata)
Cluster_Variability <- matrix(nrow=15, ncol=1)
for (i in 1:15) Cluster_Variability[i] <- kmeans(partdata,centers=i,iter.max=20, nstart=4)$tot.withinss
plot(1:15, Cluster_Variability, type="b", xlab="Number of clusters", ylab="Within groups sum of squares") ## Elbow curve or Scree plot

```

### From the above we can observe that we get an elbow at k=2, so we will perform k means clustering by taking 2 clusters.

```{r}
fit1 <- kmeans(partdata, centers=2, iter.max=20, nstart=4)
fit1
```

###Observing the different attributes, 

```{r}
fit1$cluster      
fit1$centers      
fit1$totss        
fit1$withinss     
fit1$tot.withinss 
fit1$betweenss    
fit1$size         
fit1$iter

```

### From the above, we can see that the respondents can be divided into two segments:


#### Cluster 1 prefers the Canadian and Japenese origin more than the Cluster2, while Cluster 2 prefers European more as compared to Cluster 1.

####From the price perspective, Cluster 1 prefers medium priced products more while Cluster 2 has more purchasing power and can buy high priced products as well. Both have same affinity towards buying cheap products.

#### Cluster 2 prefers Rich bodied as compared to cluster 1 , Cluster 2 prefers Regular body as compared to Cluster 1, Cluster 2 prefers Crisp and Clear body as compared to Cluster 1.

#### In terms of Aftertaste, Cluster 1 prefers Strong taste while Cluster 2 prefers Mild taste. Both have almost similar prefernce towards Very mild taste.

#### Cluster 1 consumes less Full calories when compared to Cluster 2, although Cluster 1 consumes more Regular calories when compared to Cluster 2. Both prefer low calories equally.

#### Cluster 1 prefers Four 16oz while both prefer 12 oz equally.

#### Cluster 1 prefers Brown painted glass more than Cluster 2 while, both cluster 1 and cluster 2 prefer Brown and Green glass almost equally.


### Now, proceeding further and saving the CSV,

```{r}
partdataWithClusterMember <- cbind(partdata, fit1$cluster) # append cluster membership
head(partdataWithClusterMember)

write.csv(partdataWithClusterMember,file="partdataWithClusterMember.csv")

getwd()
```




